\artus -- Framework for Event-based Data Analysis in High Energy Physics

### 2015-09-09 Core/doc/latex/paper.tex
paper: added comments for workflow section
paper: added bibliography
add todonotes package with first note
introduction sentence

\usepackage{booktabs}
\usepackage{hepnames}
\usepackage{hepunits}
\usepackage{url}

@@

\begin{abstract}
We present \artus, a data-processing framework for high energy physics experiments. \artus is designed for large-scale data analysis in a collaborative environment.
The architecture design choices take into account typical challenges and are based on experiences with similar applications.
The structure of the framework and its advantages are described.
An example usecase and performance measurements are presented.
The framework is well-tested and successfully used by several analysis groups.

\end{abstract}

@@

@@

>>>>

\usepackage{booktabs}
\usepackage{hepnames}
\usepackage{hepunits}
\usepackage{url}
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}

@@

\begin{abstract}
We present \artus, an event-by-event data-processing framework for high energy physics experiments. \artus is designed for large-scale data analysis in a collaborative environment.
The architecture design choices take into account typical challenges and are based on experiences with similar applications.
The structure of the framework and its advantages are described.
An example usecase and performance measurements are presented.
The framework is well-tested and successfully used by several analysis groups.\todo{Mention them, maybe with publications?}
\end{abstract}

@@

%Add:
% collaborative environment, high fluctuation in developers/users with wide range of programming skills (bachelor-n00b to postdoc level)
% different configurations also for one single analysis (testing etc.)

@@

\vspace{2cm}
\input{include/bib}
